Differential invariant signatures for planar Lie group transformations of images

### 2020-08-05 paper/newpaper.tex
Minor updates

For example, consider a weight $2$ transvectant defined as
\begin{align*}
    \mbox{tr} &\left[(\Omega_{12}\Omega_{12}) f(x_1, y_1)f(x_2, y_2)\right] \\
    &= \mbox{tr}\left[(\partial_{x_1 y_2} - \partial_{x_2y_1})(\partial_{x_1 y_2} -
    \partial_{x_2y_1})f(x_1, y_1)f(x_2, y_2)\right]\\
    &= \mbox{tr}\left[\left(\partial_{x_1 y_2} - \partial_{x_2 y_1}\right)\left(f_x(x_1, y_1)f_y(x_2, y_2) - f_y(x_1, y_1)f_x(x_2, y_2)\right)\right] \\
    &= \mbox{tr}\left[f_{xx}(x_1, y_1)f_{yy}(x_2, y_2) - f_{xy}(x_1, y_1)f_{xy}(x_2, y_2)\right] \\
    &= f_{xx}(x, y) f_{yy}(x, y) - f_{xy}(x, y)^2
\end{align*}
This is a degree $2$ partial transvectant as it involves derivatives of $f$
up to second order, and can be represented graphically by the following
diagram,
\begin{center}
\begin{tikzpicture}[baseline=0]
    \node[draw,circle,minimum size=0.2cm] (1) at (-0.5,0) {1};
    \node[draw,circle,minimum size=0.2cm] (2) at (0.5,0) {2};
    \draw[-] (1) to [out=30,in=150] (2);
    \draw[-] (1) to [out=-30,in=-150] (2);
\end{tikzpicture}
\end{center}
where the double edge between nodes $1$ and $2$ corresponds to the two copies of $\Omega_{12}$.
Table~\ref{tab:transvectants} shows all possible nonzero partial
transvectants of $A_2$ up to weight $4$ that can be generated in this way.
Note that the weight is the number of edges in the graph.
\begin{table}
\centering
\begin{tabular}{cccp{11cm}}
Degree & Weight & Diagram & Partial transvectant\\
\hline
2 & 2 &
\begin{tikzpicture}[baseline=0]
    \node[draw,circle,minimum size=0.2cm] (1) at (-0.5,0) {1};
    \node[draw,circle,minimum size=0.2cm] (2) at (0.5,0) {2};
    \draw[-] (1) to [out=30,in=150] (2);
    \draw[-] (1) to [out=-30,in=-150] (2);
\end{tikzpicture}
& $2 f_{xx} f_{yy} - 2 \left(f_{xy}\right)^{2}$ \\

@@

3 & 4 &
\begin{tikzpicture}[baseline=0]
    \node[draw,circle,minimum size=0.2cm] (1) at (0,1) {1};
    \node[draw,circle,minimum size=0.2cm] (2) at (-0.9511,0.3090) {2};
    \node[draw,circle,minimum size=0.2cm] (3) at (-0.5878,-.8090) {3};
    \node[draw,circle,minimum size=0.2cm] (4) at (0.5878,-.8090) {4};
    \node[draw,circle,minimum size=0.2cm] (5) at (0.9511,0.3090) {5};
    \draw[-] (1) to (2);
    \draw[-] (1) to (3);
    \draw[-] (1) to (4);
    \draw[-] (4) to (5);
\end{tikzpicture}
& $- \left(f_{x}\right)^{3} f_{yy} f_{xyy} + \left(f_{x}\right)^{3} f_{yyy} f_{xy} - \left(f_{x}\right)^{2} f_{xx} f_{y} f_{yyy} + 2 \left(f_{x}\right)^{2} f_{y} f_{yy} f_{xxy} - \left(f_{x}\right)^{2} f_{y} f_{xy} f_{xyy} + 2 f_{x} f_{xx} \left(f_{y}\right)^{2} f_{xyy} - f_{x} f_{xxx} \left(f_{y}\right)^{2} f_{yy} - f_{x} \left(f_{y}\right)^{2} f_{xy} f_{xxy} - f_{xx} \left(f_{y}\right)^{3} f_{xxy} + f_{xxx} \left(f_{y}\right)^{3} f_{xy}$ \\

4 & 4 &
\begin{tikzpicture}[baseline=0]
    \node[draw,circle,minimum size=0.2cm] (1) at (0,1) {1};
    \node[draw,circle,minimum size=0.2cm] (2) at (-0.9511,0.3090) {2};
    \node[draw,circle,minimum size=0.2cm] (3) at (-0.5878,-.8090) {3};
    \node[draw,circle,minimum size=0.2cm] (4) at (0.5878,-.8090) {4};
    \node[draw,circle,minimum size=0.2cm] (5) at (0.9511,0.3090) {5};
    \draw[-] (1) to (2);
    \draw[-] (1) to (3);
    \draw[-] (1) to (4);
    \draw[-] (1) to (5);
\end{tikzpicture}
& $\left(f_{x}\right)^{4} f_{yyyy} - 4 \left(f_{x}\right)^{3} f_{y} f_{xyyy} + 6 \left(f_{x}\right)^{2} \left(f_{y}\right)^{2} f_{xxyy} - 4 f_{x} \left(f_{y}\right)^{3} f_{xxxy} + f_{xxxx} \left(f_{y}\right)^{4}$ \\

@@

4 & 4 &
\begin{tikzpicture}[baseline=0]
    \node[draw,circle,minimum size=0.2cm] (1) at (0,0.866) {1};
    \node[draw,circle,minimum size=0.2cm] (2) at (-0.5,0) {2};
    \node[draw,circle,minimum size=0.2cm] (3) at (0.5,0) {3};
    \draw[-] (1) to [out=-150,in=90] (2);
    \draw[-] (1) to [out=-90,in=30] (2);
    \draw[-] (1) to (2);
    \draw[-] (1) to (3);
\end{tikzpicture} 
& $ f_{x} f_{xxx} f_{yyyy} - f_x f_{yyy} f_{xxxy} + 3 f_{x} f_{xyy} f_{xxyy} - 3 f_x f_{xyyy} f_{xxy} - f_{xxx} f_y f_{xyyy} + f_{xxxx} f_y f_{yyy} - 3 f_y f_{xyy} f_{xxxy} + 3 f_y f_{xxy} f_{xxyy}$ \\
\end{tabular}
\caption{Details and graphical representations of all partial transvectants up to weight $4$ of copies of a function $f$ under a transformation in $A(2)$.}
\label{tab:transvectants}
\end{table}

\todo[inline]{Put into 2 tables: order 2 + products, order 3, rest order 4. Then explain a little bit.}

\subsection{Signatures of $SA(2)$ and $A(2)$}
Recall that invariants of a supergroup are automatically invariants of any of
its subgroups. For example, invariants of $A(2)$ are automatically invariants of $SA(2)$, but not necessarily vice versa. Any of the partial transvectants found in Table~\ref{tab:transvectants} are invariants of $SA(2)$ (as the determinant is $1$) but only up to scale factor ($\det A^{-r}$) of $A(2)$.

>>>>

For example, consider a weight $2$ transvectant defined as
\begin{align*}
    \mbox{tr} &\left[(\Omega_{12}\Omega_{12}) f(x_1, y_1)f(x_2, y_2)\right] \\
    &= \mbox{tr}\left[(\partial_{x_1 y_2} - \partial_{x_2y_1})(\partial_{x_1 y_2} -
    \partial_{x_2y_1})f(x_1, y_1)f(x_2, y_2)\right]\\
    &= \mbox{tr}\left[\left(\partial_{x_1 y_2} - \partial_{x_2 y_1}\right)\left(f_x(x_1, y_1)f_y(x_2, y_2) - f_y(x_1, y_1)f_x(x_2, y_2)\right)\right] \\
    &= \mbox{tr}\left[f_{xx}(x_1, y_1)f_{yy}(x_2, y_2) - f_{xy}(x_1, y_1)f_{xy}(x_2, y_2)\right] \\
    &= f_{xx}(x, y) f_{yy}(x, y) - f_{xy}(x, y)^2
\end{align*}
This is a degree $2$ partial transvectant as it involves derivatives of $f$
up to second order, and can be represented graphically by the following
diagram,
\begin{center}
\begin{tikzpicture}[baseline=0]
    \node[draw,circle,minimum size=0.2cm] (1) at (-0.5,0) {1};
    \node[draw,circle,minimum size=0.2cm] (2) at (0.5,0) {2};
    \draw[-] (1) to [out=30,in=150] (2);
    \draw[-] (1) to [out=-30,in=-150] (2);
\end{tikzpicture}
\end{center}
where the double edge between nodes $1$ and $2$ corresponds to the two copies of $\Omega_{12}$.
Tables~\ref{tab:transvectants1} and~\ref{tab:transvectants2} shows all possible nonzero partial
transvectants of $A_2$ up to weight $4$ that can be generated in this way.
Note that the weight is the number of edges in the graph.
\begin{table}
\centering
\begin{tabular}{cccp{11cm}}
Degree & Weight & Diagram & Partial transvectant\\
\hline
2 & 2 &
\begin{tikzpicture}[baseline=0]
    \node[draw,circle,minimum size=0.2cm] (1) at (-0.5,0) {1};
    \node[draw,circle,minimum size=0.2cm] (2) at (0.5,0) {2};
    \draw[-] (1) to [out=30,in=150] (2);
    \draw[-] (1) to [out=-30,in=-150] (2);
\end{tikzpicture}
& $2 f_{xx} f_{yy} - 2 \left(f_{xy}\right)^{2}$ \\

@@

3 & 4 &
\begin{tikzpicture}[baseline=0]
    \node[draw,circle,minimum size=0.2cm] (1) at (0,1) {1};
    \node[draw,circle,minimum size=0.2cm] (2) at (-0.9511,0.3090) {2};
    \node[draw,circle,minimum size=0.2cm] (3) at (-0.5878,-.8090) {3};
    \node[draw,circle,minimum size=0.2cm] (4) at (0.5878,-.8090) {4};
    \node[draw,circle,minimum size=0.2cm] (5) at (0.9511,0.3090) {5};
    \draw[-] (1) to (2);
    \draw[-] (1) to (3);
    \draw[-] (1) to (4);
    \draw[-] (4) to (5);
\end{tikzpicture}
& $- \left(f_{x}\right)^{3} f_{yy} f_{xyy} + \left(f_{x}\right)^{3} f_{yyy} f_{xy} - \left(f_{x}\right)^{2} f_{xx} f_{y} f_{yyy} + 2 \left(f_{x}\right)^{2} f_{y} f_{yy} f_{xxy} - \left(f_{x}\right)^{2} f_{y} f_{xy} f_{xyy} + 2 f_{x} f_{xx} \left(f_{y}\right)^{2} f_{xyy} - f_{x} f_{xxx} \left(f_{y}\right)^{2} f_{yy} - f_{x} \left(f_{y}\right)^{2} f_{xy} f_{xxy} - f_{xx} \left(f_{y}\right)^{3} f_{xxy} + f_{xxx} \left(f_{y}\right)^{3} f_{xy}$ \\
\end{tabular}
\caption{Details and graphical representations of all partial transvectants up to degree $3$ of copies of a function $f$ under a transformation in $A(2)$.}
\label{tab:transvectants1}
\end{table}

\begin{table}
\centering
\begin{tabular}{cccp{11cm}}
Degree & Weight & Diagram & Partial transvectant\\
\hline
4 & 4 &
\begin{tikzpicture}[baseline=0]
    \node[draw,circle,minimum size=0.2cm] (1) at (0,1) {1};
    \node[draw,circle,minimum size=0.2cm] (2) at (-0.9511,0.3090) {2};
    \node[draw,circle,minimum size=0.2cm] (3) at (-0.5878,-.8090) {3};
    \node[draw,circle,minimum size=0.2cm] (4) at (0.5878,-.8090) {4};
    \node[draw,circle,minimum size=0.2cm] (5) at (0.9511,0.3090) {5};
    \draw[-] (1) to (2);
    \draw[-] (1) to (3);
    \draw[-] (1) to (4);
    \draw[-] (1) to (5);
\end{tikzpicture}
& $\left(f_{x}\right)^{4} f_{yyyy} - 4 \left(f_{x}\right)^{3} f_{y} f_{xyyy} + 6 \left(f_{x}\right)^{2} \left(f_{y}\right)^{2} f_{xxyy} - 4 f_{x} \left(f_{y}\right)^{3} f_{xxxy} + f_{xxxx} \left(f_{y}\right)^{4}$ \\

@@

4 & 4 &
\begin{tikzpicture}[baseline=0]
    \node[draw,circle,minimum size=0.2cm] (1) at (0,0.866) {1};
    \node[draw,circle,minimum size=0.2cm] (2) at (-0.5,0) {2};
    \node[draw,circle,minimum size=0.2cm] (3) at (0.5,0) {3};
    \draw[-] (1) to [out=-150,in=90] (2);
    \draw[-] (1) to [out=-90,in=30] (2);
    \draw[-] (1) to (2);
    \draw[-] (1) to (3);
\end{tikzpicture} 
& $ f_{x} f_{xxx} f_{yyyy} - f_x f_{yyy} f_{xxxy} + 3 f_{x} f_{xyy} f_{xxyy} - 3 f_x f_{xyyy} f_{xxy} - f_{xxx} f_y f_{xyyy} + f_{xxxx} f_y f_{yyy} - 3 f_y f_{xyy} f_{xxxy} + 3 f_y f_{xxy} f_{xxyy}$ \\
\end{tabular}
\caption{Details and graphical representations of all partial transvectants of weight $4$ of copies of a function $f$ under a transformation in $A(2)$.}
\label{tab:transvectants2}
\end{table}

\todo{Explain}

\subsection{Signatures of $SA(2)$ and $A(2)$}
Recall that invariants of a supergroup are automatically invariants of any of
its subgroups. For example, invariants of $A(2)$ are automatically invariants of $SA(2)$, but not necessarily vice versa. Any of the partial transvectants found in Tables~\ref{tab:transvectants1} and~\ref{tab:transvectants2} are invariants of $SA(2)$ (as the determinant is $1$) but only up to scale factor ($\det A^{-r}$) of $A(2)$.
